	% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
\usepackage{csquotes}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
}
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{NAME\\ [12pt]} % the \\[12pt] adds a blank line after name
 
\address{
%{\bf Present Address} \\ Carrer Consell de cent, 391,4,2 \\ Barcelona, Spain, 08009.  \\
 Skype\ :\ rahulkumar.gayatri\\
 email\ :\ rahulgayatri84@gmail.com\\
% phone-number\ :\ +34-6996901960
 }
%\address{{\bf Permanent Address} \\ Flat No: 601, Dream Home Palace, Green Hills Colony road no. 1\\ Kothapet, hyd 500035, Telangana, India}

 
\begin{resume} 
%\section{A short introduction}
%%For Deutche Bank. 
%The multidiscplinary and challanging area of computer science has taught me to find innovative and efficient solutions to a given problem. 
%Work in R\&D did not only provide an in depth-knowledge in the areas of mathematics, engineering and CS, but has also given me valuable insight into problem analysis, solution design, rapid prototyping as well as into effective collabortion with other engineers.
%%My objective is to use the analytical and problem solving skills acquired during the course of my studies in finding solution to a given problem. 
%My objective is to explore career opportunities in diverse fields and apply there the knowledge gained from my education. 
%%
%\section{Objective} 
%To work in the field of High Performance Computing and parallel programming so that I can use my previous knowledge and experience. 
%I would like to work on finding innovative methods to parallelize algorithms so that they can take better advantage of the rapidly growing hardware performance. 
%I am interested in the development of compiler and runtimes for parallel programming models.
%
\section{Research Interest}
\mbox{} \newline
%For Mattias, objective of the CV
%To work on challenging projects and be a part of the latest trending developments in the world of technology. 
%
%
%Below is generic objective for just C and in regular...
To work in the area of developing efficient algorithms that make the optimum use of the available resources. 
To work on performance optimizations of benchmarks (tracing applications for performance bottlenecks and overcome them with elegant solutions). 
To work on challenging projects and be a part of the latest trending developments in the world of technology. 
%
%
%Below is the generic Objective.
%
%To work in the field of High Performance Computing, to develop innovative methods for parallelizing algorithms. 
%My research interest lie in the areas of Parallel Programming, Transactional Memory(STM), Programming Models (Compiler and Runtime development), Performance Optimizations of HPC benchmarks (Tracing applications for performance bottlenecks and overcome them with efficient and elegant solutions). 
%
%Conduct research in the areas of something useful i.e., I can see it applicable in daily life. Work on something that does not make me feel \enquote{Oh GOD do I have to go to office today too...} every morning. 
%Collaborate with colleagues who inspire me to learn and expand my knowledge. 
%
%
\section{Education} 
%\mbox{} \newline
{\bf Doctor of Philosophy (PhD)  in Computer Science } (2015) \\
Barcelona Supercomputing Center \\
Thesis Title - \enquote{Increasing Parallelism through Speculation in Task-Based Programming Model.}\\
Web-page - \url{http://www.bsc.es/}\\\\
%
{\bf Master of Technology }(2009) \\
Specialization in Computer Science. \\
Sri Sathya Sai University \\
Web-page - \url{http://sssihl.edu.in/sssuniversity/Academics/DepartmentofMathematicsComputerScience/Overview.aspx}\\\\
%
{\bf Master of Science }(2007) \\
Specialization in Computer Science. \\
Sri Sathya Sai University \\\\
%
{\bf Bachelor of Science} (2005) \\
Specialization in Mathematics. \\
Sri Sathya Sai University \\\\
%
%
%Publications with links
\section{Publications}
%Enumerating papers so as to reference later in projects. 
%
1] \enquote{Loop level speculation in a task based programming model.} \\
        \url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6799132&url=http\%3A\%2F\%2Fieeexplore.ieee.org\%2Fxpls\%2Fabs\_all.jsp\%3Farnumber\%3D6799132}\\
%
2] \enquote{Transactional access to shared memory in StarSs, a task based programming model.} \\
        \url{http://link.springer.com/chapter/10.1007/978-3-642-32820-6\_51#page-1} \\
%
3] \enquote{Analysis of the overheads incurred due to speculation in a task based programming model.} \\
        \url{http://research.ac.upc.edu/multiprog/papers/multiprog-2015-3.pdf} \\
%
4] \enquote{TERAFLUX: Harnessing dataflow in next generation teradevices.} \\
        \url{http://www.sciencedirect.com/science/article/pii/S0141933114000490} \\
%
%Publications without links
%\section{Publications}
%%Enumerating papers so as to reference later in projects. 
%%
%1] \enquote{Loop level speculation in a task based programming model.} High Performance Computing (HiPC), 2013 20th International Conference on. IEEE, 2013.\\
%        authors - \name{}{Rahulkumar Gayatri, Rosa M.Badia, Eduard Ayguade, et.al}\\\\
%%
%2] \enquote{Transactional access to shared memory in StarSs, a task based programming model.} Euro-Par 2012 Parallel Processing. Springer Berlin Heidelberg.\\
%        authors - \name{}{Rahulkumar Gayatri, Rosa M.Badia and Eduard Ayguade}\\\\
%%
%3] \enquote{Analysis of the overheads incurred due to speculation in a task based programming model.} Programmability Issues for Heterogeneous Multicores (MULTIPROG-2015). \\
%        authors - \name{}{Rahulkumar Gayatri, Rosa M.Badia and Eduard Ayguade}\\\\
%%
%4] \enquote{TERAFLUX: Harnessing dataflow in next generation teradevices.} Microprocessors and Microsystems (2014). \\\\
%
%
\section{Projects} 
{\bf Doctoral Thesis} \\
%A detailed analysis of speculation based optimistic techniques for synchronization of multiple threads in parallel programing. 
Research  the idea of integrating Transactional Memory into a Parallel Programming Model and use the framework to synchronize the multiple threads of execution. 
This optimistic approach has been adopted to improve the performance and the efficiency of a parallel application.\\ 
Papers published in this project: papers [1],[2] and [3] .\\\\
%
{\bf StarSs}\\
A task-based programming model to make parallel programming easier. It generates a task-dependency graph at runtime based on the data-flow principles. 
My contribution to the thesis was to introduce new directives to the compiler and provide the required runtime support for the synchronization of multiple threads. \\\\
%
{\bf Teraflux}  \\
Teraflux project proposes a set of programming model, compiler analysis and a scalable, reliable architecture that will be able to harness such large scale parallelism in an efficient way.
My contribution to the project was to introduce STM-based concurrency to handle simultaneous access to shared memory.\\
Papers published in this project: paper [4].\\\\
%
{\bf MTech Thesis} \\
An efficient Breadth First Search (BFS) implementation that exploits memory locality in the IBM's Cell.B.E architecture. \\ 
A poster presenting this work was published in the student research symposium of HiPC 2008, Banglore, India.
%\newline\newline
%
\section{Professional Career}
%
%\mbox{} \newline
Doctoral student at Barcelona Supercomputing Center - \\ 
September, 2009 - Present day
%
\section{Honors} 
Received a Pre-Doctoral scholarship, FI AGAUR grant,  by Generalitat de Catalunya

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Programming Languages and Models}
   \begin{tabular}{l p{3in}}
    \underline{Languages:} & C\smallskip ,C++ \smallskip \\
	\underline{Scripting:} & Shell\smallskip, LaTeX\smallskip , Sed\smallskip, awk\smallskip, gnuplot\\
	\underline{Programming Models:} & StarSs\smallskip, OpenMP\smallskip , MPI\smallskip, Software Transactional Memory (STM)\\\\
%	\underline{Office:} & Microsoft Office\smallskip, LibreOffice\\
	\underline{Operating Systems:}  & Microsoft Windows\smallskip , Linux\\
    \underline{Software:} & Eclipse, Visual Studio 2010\smallskip, GIT\smallskip\\
    \underline{Profiling Tools:} &gdb, Valgrind\smallskip \\ 
 \end{tabular}
%
\section{Languages}
English, Hindi, Spanish.
%Telugu, Marathi. 
\section{References}
%
{\it Rosa Maria Badia}, Project and group manager at Barcelona Supercomputing Center.\\ 
Relation: PhD supervisor, email: \href{}{rosa.m.badia@bsc.es},\\
Web-page: \url{http://personals.ac.upc.es/rosab/}\\\\ 
%
{\it Eduard Ayguadè}, Computer Sciences Department Associate Director at Barcelona Supercomputing Center.\\ 
Relation: PhD supervisor, email: \href{}{eduard.ayguade@bsc.es},\\
Web-page: \url{http://people.ac.upc.es/eduard/}\\\\ 
%
{\it Pieter Bellens}, Senior researcher at Barcelona Supercomputing Center.\\
Relation: Present colleague, email: \href{}{pbellens@gmail.com} \\\\
%
\end{resume} 
%
\end{document} 


