	% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{csquotes}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=blue,
}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

%\name{NAME\\ [12pfasl://www.amazon.com/End-Times-Bram-Ben-TP/dp/1607069415t]} % the \\[12pt] adds a blank line after name
%
\name {Rahulkumar Gayatri}
\address{
email\ :\ rahulgayatri84@gmail.com\\
phone-number\ :\ +1-9253848354
}
%\address{{\bf Permanent Address} \\ Flat No: 601, Dream Home Palace, Green Hills Colony road no. 1\\ Kothapet, hyd 500035, Telangana, India}

\begin{resume}
%
    \section{Current Position }
    \begin{itemize}
        \item \textbf{\textit{\textrm{Title}}} - Exascale Science Application PostDoctoral Fellow. \\
            Lawrence Berkeley National Lab.
        \item \textbf{\textit{\textrm{Description}}} - HPC Application Optimization Engineer and Performance Portable Application Developer.
    \end{itemize}
%
% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
%
\section{Projects}
\begin{itemize}
%
    \item \textbf{\textit{\textrm{{Berkeley GW}}}} \\
        - Material science kernel used as a case study for performance portability.\\
        - Implemented KNL and GPU specific code and compared the performance with their OpenMP4.5x and Kokkos implementations.\\
        \url{http://performanceportability.org/case_studies/gw/}
%
    \item \textbf{\textit{\textrm{{SW4}}}} -
            Optimized the code for Intel's Knight landing architecture by enabling vectorization, cache blocking and reducing OpenMP overhead.\\
            \url{https://github.com/geodynamics/sw4lite}
%
    \item \textbf{\textit{\textrm{{MOOSE}}}} -
           Parallelize and optimize the ODE system solvers used to simulate cellular behaviour in human brain.\\
           \url{https://moose.ncbs.res.in/}
%
    \item \textbf{\textit{\textrm{{Doctoral Thesis:  OMPSs}}}} -
           Compiler and runtime support for multiple threads in OMPSs.
%
%	   \item {\bf Master Thesis} -
%		An efficient Breadth First Search (BFS) implementation that exploits memory locality in the IBM's Cell.B.E architecture.
%
\end{itemize}


\section{Proficiencies}
\begin{itemize}
    \item \textbf{\textit {Languages}:} C,C++ , python
    \item \textbf{\textit {Programming Models}:} OpenMP4.5, OpenMP3.0, Cuda, Kokkos, OMPSs, Pthreads, MPI, STM
    \item \textbf{\textit {Scripting}:} Shell, LaTeX, Sed, awk, gnuplot
    \item \textbf{\textit {Profiling Tools}:} Intel-vtune, Intel-advisor, Intel-SDE, LIKWID, gdb, Valgrind
\end{itemize}
%
\section{Publications}
%Enumerating papers so as to reference later in projects.
%
\begin{itemize}
	   \item \enquote{Loop level speculation in a task based programming model.}
           \textit{High Performance Computing (HiPC), 2013 20th International Conference}
%
	   \item \enquote{Transactional access to shared memory in StarSs, a task based programming model.}
           \textit{Euro-par, 2012 Parallel Processing}
%
	   \item \enquote{Analysis of the overheads incurred due to speculation in a task based programming model.}
           \textit{MULTIPROG, workshop at HiPEAC, 2015}
%
	   \item \enquote{TERAFLUX: Harnessing dataflow in next generation teradevices.}
           \textit{Microprocessors and Microsystems}
%
	   \item \enquote{Parallelizing Breadth First Search Using Cell BE, HiPC, Student Symposium, 2008}
%
\end {itemize}
\section{Education}
%
\begin{itemize}
	   \item {\bf Doctor of Philosophy (PhD)  in Computer Science } (2015) \\
		\enquote{Increasing Parallelism through Speculation in Task-Based Programming Model.}
%
    \item {\bf Master of Technology, Computer Science } {\textit GPA - 4.75/5.00} (2009)
%
\end{itemize}
%
%\section{Professional Career}
%%
%\begin{itemize}
%    \item - * Postdoc at Lawrence Berkeley National Lab.
%	\item - Technical Specialist, High Performance Computing (HPC), Wipro Infotech
%\end{itemize}
%
        \section{linkedin} \url{https://www.linkedin.com/in/rahulgayatri/}
\end{resume}
%
\end{document}


